Draft 1

### 2012-05-11 Thesis - Presentation/draft1.tex
FRI May 11th 2012 12:21

\subsection{First Case}
In the first case, we define the potential as a finite well of strength $0.1$ with support in $4 \leq x \leq 6$,
\begin{equation}\label{potentialdef1}
V = \begin{cases}
-0.1 &\mbox{} 4\leq x\leq 6\\
0 &\mbox{ otherwise}
\end{cases} 
\end{equation}

\begin{figure}[ht]
\centering
\includegraphics[width=225pt, height=150pt]{potential1d1.png}
\caption[\textwidth]{Test Potential 1}
% 
% \centering
% \includegraphics[width=225pt, height=150pt]{potential1d2.png}
% \caption[\textwidth]{Test Potential 2}
\end{figure}

The Born Series is calculated for $15$ iterations. The Hamiltonian is modified using the operator defined in \eqref{potmod} with
$\lambda=1$.  We also set $\epsilon=0.1$.

@@

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series1a.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series1b.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series1c.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

We see that the Born Series converges to the exact value in both cases. It is also to be noted that the 
.

\subsection{Second Case}
In the second case, we define the potential as, 
\begin{equation}\label{potentialdef2}
V = \begin{cases}
-0.5 &\mbox{} 4\leq x\leq 6\\
0 &\mbox{ otherwise}
\end{cases} 
\end{equation}

\begin{figure}[hb]
\centering
\includegraphics[width=225pt, height=150pt]{potential1d2.png}
\caption[\textwidth]{Test Potential 2}
\end{figure}

@@

We see that for the original Hamiltonian, the Born series converges in some cases but doesn't in others. However,
with the modification, we always have convergence at a faster rate.
\subsection{Third Case}
\begin{equation}\label{potentialdef2}
V = -200\mathtt{exp}(-(x-3.5)^2/0.5)-200\mathtt{exp}(-(x-6.5)^2/0.5)
\end{equation}

>>>>

\subsection{First Case}
In the first case, we define the potential as a finite well of strength $0.1$ with support in $4 \leq x \leq 6$,
\begin{equation}\label{potentialdef1}
V = \begin{cases}
-0.1 &\mbox{} 4\leq x\leq 6\\
0 &\mbox{ otherwise}
\end{cases} 
\end{equation}
\begin{center}
\begin{figure}[htb]
\includegraphics[width=360pt, height=175pt]{series1a.png}
\includegraphics[width=360pt, height=175pt]{series1b.png}
\includegraphics[width=360pt, height=175pt]{series1c.png}
\caption[\textwidth]{First Case - Weak Finite Well}
\end{figure}
\end{center}
The Born Series is calculated for $15$ iterations. The Hamiltonian is modified using the operator defined in \eqref{potmod} with
$\lambda=1$.  We also set $\epsilon=0.1$.

@@

\subsection{Second Case}
In the second case, we define the potential as, 
\begin{equation}\label{potentialdef2}
V = \begin{cases}
-0.5 &\mbox{} 4\leq x\leq 6\\
0 &\mbox{ otherwise}
\end{cases} 
\end{equation}
i.e., a finite well of strength $0.5$ with support in $4 \leq x \leq 6$,

@@

We see that for the original Hamiltonian, the Born series converges in some cases but doesn't in others. However,
with the modification, we always have convergence at a faster rate.
\subsection{Third Case}
\begin{equation}\label{potentialdef3}
V = -200\mathtt{exp}(-(x-3.5)^2/0.5)-200\mathtt{exp}(-(x-6.5)^2/0.5)
\end{equation}

\begin{figure}[hb]
\centering
\includegraphics[width=225pt, height=150pt]{potential1d2.png}
\caption[\textwidth]{Test Potential 3}
\end{figure}
